PREPRINT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- PREPRINT.

### 2024-03-05 docs/_tex/index.tex
add conclusion

\renewcommand\refname{Conclusion}
  \bibliography{library.bib}

>>>>

\section{Conclusion}\label{conclusion}

The utilization of drone-based remote sensing coupled with machine
learning techniques has proven to be an effective method for the
discrimination of seagrasses and macroalgae in coastal ecosystems. This
study has highlighted the potential for these technologies to enhance
the accuracy and efficiency of habitat monitoring, which is essential
for environmental management and conservation strategies. Through the
application of high-resolution multispectral imagery, the research
contributes to the broader understanding and surveillance of aquatic
ecosystems, aligning with objectives outlined in policies such as the
Water Framework Directive. The findings underscore the importance of
adopting advanced remote sensing tools in ecological studies and
environmental monitoring, providing a foundation for future research and
policy implementation aimed at ecosystem preservation and restoration.

  \bibliography{library.bib}

### 2024-03-05 index.qmd
add conclusion

>>>>

The utilization of drone-based remote sensing coupled with machine learning techniques has proven to be an effective method for the discrimination of seagrasses and macroalgae in coastal ecosystems. This study has highlighted the potential for these technologies to enhance the accuracy and efficiency of habitat monitoring, which is essential for environmental management and conservation strategies. Through the application of high-resolution multispectral imagery, the research contributes to the broader understanding and surveillance of aquatic ecosystems, aligning with objectives outlined in policies such as the Water Framework Directive. The findings underscore the importance of adopting advanced remote sensing tools in ecological studies and environmental monitoring, providing a foundation for future research and policy implementation aimed at ecosystem preservation and restoration.
